A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-06-22 talk_Roscoff.tex
liquid in lightgray use relative positionning in pathsX

			%\draw[->] (x.base) --(rel axis cs:0.98,0.01);
		\end{groupplot}
		\node[anchor=north west, rotate=90, inner xsep=0,lightgray] (x) at (g c1r2.south east) {crystal};
		%\draw(g c1r1.outer south west) -- +(\textwidth,0);
		\end{tikzpicture}
		\column{0.5\textwidth}
		%Small polymer/colloid size ratio
		\structure{Dynamic assymetry}
		\tikzsetnextfilename{vps}%
		\begin{tikzpicture}
	\draw[->] (0,0) -- +(\textwidth,0) node[pos=0.05, label=-90:\textcolor{ilmorange}{$\tau_1$}](t1) {|} node[pos=0.54, label=-90:\textcolor{ilmcolor}{$\tau_2$}] (t2){|} coordinate[pos=1] (tf) node[anchor=north east,font=\footnotesize]{time};
	\node[below, font=\scriptsize, text width=0.4\textwidth, align=center] at ($(t1)!0.5!(t2)$) {continuous \textcolor{ilmcolor}{minority} phase};
	\let\side\relax
	\newlength\side
	\setlength{\side}{0.275\textwidth}
	\fill[ilmcolor!80!ilmorange] ($(t1)!0.1!45:(t2)$) coordinate(cse) rectangle +(\side,\side) coordinate(cnw);
	\begin{scope}
	\clip (cse) rectangle (cnw);
	\fill[ilmorange!80!ilmcolor] ++($(cse)!0.5!(cnw)$) 
		+(60:0.3\side) circle (0.22\side) 
		+(180:0.3\side) circle (0.22\side) 
		+(-60:0.3\side) circle (0.22\side) 
		+(0:0.6\side) circle (0.22\side)
		+(120:0.6\side) circle (0.22\side)
		+(-120:0.6\side) circle (0.22\side)
		+(45:0.8\side) circle (0.22\side)
		+(-45:0.8\side) circle (0.22\side);
	\end{scope}
	\fill[ilmcolor] (cse-|t2) ++(-0.5\side,0) coordinate(cse) rectangle +(\side,\side) coordinate(cnw);
	\begin{scope}
	\clip (cse) rectangle (cnw);
	\fill[ilmorange] ++($(cse)!0.5!(cnw)$) 
		+(60:0.3\side) circle (0.26\side) 
		+(180:0.3\side) circle (0.26\side) 
		+(-60:0.3\side) circle (0.25\side) 
		+(0:0.6\side) circle (0.25\side)
		+(120:0.6\side) circle (0.25\side)
		+(-120:0.6\side) circle (0.25\side)
		+(45:0.8\side) circle (0.25\side)
		+(-45:0.8\side) circle (0.25\side)
		%enhance broken bond
		+(120:0.15\side) circle (0.07\side);
	\end{scope}
	\fill[ilmorange] (cse-|tf) ++(-\side,0) coordinate(cse) rectangle +(\side,\side) coordinate(cnw);
	\begin{scope}
	\clip (cse) rectangle (cnw);
	\fill[ilmcolor] ++($(cse)!0.5!(cnw)$) circle (0.07\side)
		+(0:0.3\side) circle (0.07\side) 
		+(120:0.3\side) circle (0.07\side) 
		+(-120:0.3\side) circle (0.07\side) 
		+(-60:0.6\side) circle (0.07\side)
		+(60:0.6\side) circle (0.07\side)
		++(0:0.3\side)
		+(-60:0.3\side) circle (0.07\side)
		+(60:0.3\side) circle (0.07\side)
		+(120:0.6\side) circle (0.07\side)
		+(-120:0.6\side) circle (0.07\side)
		++(180:0.9\side)
		+(-60:0.3\side) circle (0.07\side)
		+(60:0.3\side) circle (0.07\side);
	\end{scope}
	\end{tikzpicture}
	\begin{itemize}
		\item viscoelastic phase sep.\\ \hfill\textit{\footnotesize Tanaka J.Phys.Cond.Mat.~2000}
		\pause
		\item glass transition $\textcolor{ilmcolor}{\tau_2} \rightarrow +\infty$
		\item arrested phase separation
		\item spinodal + glass $\Rightarrow$ gel\\ \hfill\textit{\footnotesize Lu et al. Nature~2008}
	\end{itemize}	
	\end{columns}
\end{frame}

@@

\begin{frame}{Dynamics: Bergeron > Ostwald}
	\vspace{\baselineskip}
	\begin{center}
	\tikzsetnextfilename{pathsX}\vspace{-0.5em}\input{presentation/pathsX.pgf}
	\end{center}
	\begin{columns}
	\column{0.5\textwidth}
	\begin{itemize}
	\item Individual trajectories
	\item Probability of path to X
	\end{itemize}
	\column{0.5\textwidth}
	\tikzsetnextfilename{pathsX2}%
	\begin{tikzpicture}
	\node[regular polygon, regular polygon sides=3, minimum width=5em] (tri){};
	\node[circle, minimum width=3.5em, fill=green!40, left=1em of tri.corner 2] (gas) {gas};
	\node[circle, minimum width=3.5em, draw, fill=white, right =1em of tri.corner 3] (liq) {liquid};
	\node[regular polygon, regular polygon sides=6, fill=red,minimum width=3.5em, inner sep=0, above=0 of tri.corner 1] (X) {crystal};
	\draw[->, very thick] ($(tri.corner 2)+(0,0.25em)$) -- ($(liq.west)+(0,0.25em)$) node[midway, above]{54\%}-- (X);
	\draw[->, very thick, dotted] ($(tri.corner 3)+(0,-0.25em)$) -- ($(gas.east)+(0,-0.25em)$) node[midway, below]{35\%}-- (X);
	\draw[->, very thick, dashed] (X) edge [in=190,out=-130,loop] node[left]{11\%} ();
	\end{tikzpicture}
	\end{columns}
\end{frame}

>>>>

			%\draw[->] (x.base) --(rel axis cs:0.98,0.01);
		\end{groupplot}
		\node[anchor=north west, rotate=90, inner xsep=0,lightgray] (x) at (g c1r2.south east) {crystal};
		%\draw(g c1r1.outer south west) -- +(\textwidth,0);
		\end{tikzpicture}
		\column{0.5\textwidth}
		%Small polymer/colloid size ratio
		\structure{Dynamic assymetry}
		\tikzsetnextfilename{vps}%
		\begin{tikzpicture}
	\draw[->] (0,0) -- +(\textwidth,0) node[pos=0.05, label=-90:\textcolor{ilmorange}{$\tau_1$}](t1) {|} node[pos=0.54, label=-90:\textcolor{ilmcolor}{$\tau_2$}] (t2){|} coordinate[pos=1] (tf) node[anchor=north east,font=\footnotesize]{time};
	\node[below, font=\scriptsize, text width=0.4\textwidth, align=center] at ($(t1)!0.5!(t2)$) {continuous \textcolor{ilmcolor}{minority} phase};
	\node[below, font=\scriptsize, text width=0.3\textwidth, align=center] at ($(t2)!0.4!(tf)$) {phase inversion};
	\let\side\relax
	\newlength\side
	\setlength{\side}{0.275\textwidth}
	\fill[ilmcolor!80!ilmorange] ($(t1)!0.1!45:(t2)$) coordinate(cse) rectangle +(\side,\side) coordinate(cnw);
	\begin{scope}
	\clip (cse) rectangle (cnw);
	\fill[ilmorange!80!ilmcolor] ++($(cse)!0.5!(cnw)$) 
		+(60:0.3\side) circle (0.22\side) 
		+(180:0.3\side) circle (0.22\side) 
		+(-60:0.3\side) circle (0.22\side) 
		+(0:0.6\side) circle (0.22\side)
		+(120:0.6\side) circle (0.22\side)
		+(-120:0.6\side) circle (0.22\side)
		+(45:0.8\side) circle (0.22\side)
		+(-45:0.8\side) circle (0.22\side);
	\end{scope}
	\fill[ilmcolor] (cse-|t2) ++(-0.5\side,0) coordinate(cse) rectangle +(\side,\side) coordinate(cnw);
	\begin{scope}
	\clip (cse) rectangle (cnw);
	\fill[ilmorange] ++($(cse)!0.5!(cnw)$) 
		+(60:0.3\side) circle (0.26\side) 
		+(180:0.3\side) circle (0.26\side) 
		+(-60:0.3\side) circle (0.25\side) 
		+(0:0.6\side) circle (0.25\side)
		+(120:0.6\side) circle (0.25\side)
		+(-120:0.6\side) circle (0.25\side)
		+(45:0.8\side) circle (0.25\side)
		+(-45:0.8\side) circle (0.25\side)
		%enhance broken bond
		+(120:0.15\side) circle (0.07\side);
	\end{scope}
	\fill[ilmorange] (cse-|tf) ++(-\side,0) coordinate(cse) rectangle +(\side,\side) coordinate(cnw);
	\begin{scope}
	\clip (cse) rectangle (cnw);
	\fill[ilmcolor] ++($(cse)!0.5!(cnw)$) circle (0.07\side)
		+(0:0.3\side) circle (0.07\side) 
		+(120:0.3\side) circle (0.07\side) 
		+(-120:0.3\side) circle (0.07\side) 
		+(-60:0.6\side) circle (0.07\side)
		+(60:0.6\side) circle (0.07\side)
		++(0:0.3\side)
		+(-60:0.3\side) circle (0.07\side)
		+(60:0.3\side) circle (0.07\side)
		+(120:0.6\side) circle (0.07\side)
		+(-120:0.6\side) circle (0.07\side)
		++(180:0.9\side)
		+(-60:0.3\side) circle (0.07\side)
		+(60:0.3\side) circle (0.07\side);
	\end{scope}
	\end{tikzpicture}
	\begin{itemize}
		\item viscoelastic phase sep.\\ \hfill\textit{\footnotesize Tanaka J.Phys.Cond.Mat.~2000}
		\pause
		\item glass transition $\textcolor{ilmcolor}{\tau_2} \rightarrow +\infty$
		\item arrested phase separation
		\item spinodal + glass $\Rightarrow$ gel\\ \hfill\textit{\footnotesize Lu et al. Nature~2008}
	\end{itemize}	
	\end{columns}
\end{frame}

@@

\begin{frame}{Dynamics: Bergeron > Ostwald}
	\vspace{\baselineskip}
	\begin{center}
	\tikzsetnextfilename{pathsX}\vspace{-0.5em}\input{presentation/pathsX.pgf}
	\end{center}
	\begin{columns}
	\column{0.5\textwidth}
	\begin{itemize}
	\item Individual trajectories
	\item Probability of path to X
	\end{itemize}
	\column{0.5\textwidth}
	\tikzsetnextfilename{pathsX2}%
	\begin{tikzpicture}
	\colorlet{gas}{green!40}%
	\colorlet{crystal}{red}%
	\colorlet{liquid}{lightgray}%
	\node[regular polygon, regular polygon sides=3, minimum width=5em] (tri){};
	\node[circle, minimum width=3.5em, fill=gas, left=1em of tri.corner 2] (gas) {gas};
	\node[circle, minimum width=3.5em, fill=liquid, right =1em of tri.corner 3] (liq) {liquid};
	\node[regular polygon, regular polygon sides=6, fill=crystal,minimum width=3.5em, inner sep=0, above=0 of tri.corner 1] (X) {crystal};
	\draw[->, very thick] ($(tri.corner 2)+(0,0.25em)$) -- ($(liq.west)+(0,0.25em)$) node[midway, above]{54\%}-- (X);
	\draw[->, very thick, dotted] ($(tri.corner 3)+(0,-0.25em)$) -- ($(gas.east)+(0,-0.25em)$) node[midway, below]{35\%}-- (X);
	\draw[->, very thick, dashed] (X) edge [in=190,out=-130,loop] node[left]{11\%} ();
	\end{tikzpicture}
	\end{columns}
\end{frame}
